MSDS6372Project1

### 2021-01-31 MSDS6372Project1.Rmd
Fixing Flex Fuel section

str(CarData)
# Use For loop to fill in Yes/No to each Market Category column
for(j in 1:dim(marketCat)[1]){
  CarData[marketCat[j,1]] = ifelse(grepl(marketCat[j,1],CarData$Market.Category),"Yes","No")
}
# Performance is being handled individually...
CarData$Performance = ifelse(grepl("Performance",CarData$Market.Category)&(!grepl("High-Performance",CarData$Market.Category)),"Yes","No")

@@

# Look at summary of data
summary(CarData$VehicleStyle)
str(CarData)
# Look at missing Data if any
# missingData = CarData[rowSums(is.na(CarData)) > 0,]
# missingData
# dim(missingData)
write.csv(CarData,"CleanedCarData.csv",row.names = FALSE)

@@

```{r}
# Explore numerical variables
train %>% select(MSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity)%>%ggpairs()
# Try Log transformation on MSRP see if it will improve correlations
train$logMSRP = log(train$MSRP)
train %>% select(logMSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity)%>%ggpairs()
# It looks like logMSRP has increased correlation with Year but decreased correlation with EngineHP, EngineCylinders
# It's best to run LASSO and choose predictors on both with transformation and without Log transformation in order to identify which
# Model performs better
train = train[,-27]
#str(train)
library(glmnet)
library(car)
# Since we want a easy to interperate model, we don't want to use predictor Make and Model that has too many levels in the model
train = train[,-(1:2)]
str(train)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- log(train$MSRP)
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at coefficients
coef(cv.out, cv.out$lambda.min)
# Seems like LASSO has selected all predictors, only few levels within EngineFuel, TransmissionType, VehicleStyle got turned off
# Build model with predictors LASSO selected
log.model1 = lm(log(MSRP)~.,data=train)
# Check VIF
summary(log.model1)
# TransmissionType and Hatchback provides NA on summary statistic, try remove them as predictors
log.model2 = lm(log(MSRP)~.- TransmissionType - Hatchback,data=train)
summary(log.model2)
# Look at VIF
vif(log.model2)[,3]^2
# CityMPG has really high VIF remove it from model
log.model3 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG,data=train)
# Look at VIF
vif(log.model3)[,3]^2
# NumberOfDoors has really high VIF remove from model
log.model4 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG - NumberOfDoors,data=train)
# Look at VIF
vif(log.model4)[,3]^2
# HighwayMPG still have over 10 VIF, remove from model
log.model5 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG - NumberOfDoors - HighwayMPG,data=train)
vif(log.model5)[,3]^2
# Diesel is not significant, HighPerformance is not significant, Performance is not significant Remove from simple model
log.model6 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG - NumberOfDoors - HighwayMPG - Diesel - HighPerformance - Performance,data=train)
vif(log.model6)[,3]^2
# N_A is still not significant, remove from model
log.model7 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG - NumberOfDoors - HighwayMPG - Diesel - HighPerformance - Performance - N_A,data=train)
vif(log.model7)[,3]^2
summary(log.model7)
# Model 7 is a highly interpretable model with decent R-squared.

>>>>

str(CarData)
# Use For loop to fill in Yes/No to each Market Category column
for(j in 1:dim(marketCat)[1]){
  CarData[marketCat[j,1]] = ifelse(grepl(marketCat[j,1],CarData$Market.Category),"Yes","No")
}
# Performance is being handled individually...
CarData$Performance = ifelse(grepl("Performance",CarData$Market.Category)&(!grepl("High-Performance",CarData$Market.Category)),"Yes","No")
# Flex Fuel column if EngineFuelType has flex-fuel
CarData$`Flex Fuel` = ifelse(grepl("flex-fuel",CarData$Engine.Fuel.Type)&CarData$`Flex Fuel`=="No","Yes",CarData$`Flex Fuel`)

@@

# Look at summary of data
str(CarData)
# Look at missing Data if any
# missingData = CarData[rowSums(is.na(CarData)) > 0,]
# missingData
# dim(missingData)
write.csv(CarData,"CleanedCarData.csv",row.names = FALSE)

@@

```{r}
# Explore numerical variables
train %>% select(MSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity)%>%ggpairs()
# Try Log transformation on MSRP see if it will improve correlations
train$logMSRP = log(train$MSRP)
train %>% select(logMSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity)%>%ggpairs()
# It looks like logMSRP has increased correlation with Year but decreased correlation with EngineHP, EngineCylinders
# It's best to run LASSO and choose predictors on both with transformation and without Log transformation in order to identify which
# Model performs better
train = train[,-27]
#str(train)
library(glmnet)
library(car)
# Since we want a easy to interperate model, we don't want to use predictor Make and Model that has too many levels in the model
train = train[,-(1:2)]
str(train)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- log(train$MSRP)
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at coefficients
coef(cv.out, cv.out$lambda.min)
# Seems like LASSO has selected all predictors, only few levels within EngineFuel, TransmissionType, VehicleStyle got turned off
# Build model with predictors LASSO selected
log.model1 = lm(log(MSRP)~.,data=train)
# Check VIF
summary(log.model1)
# TransmissionType and Hatchback provides NA on summary statistic, try remove them as predictors
log.model2 = lm(log(MSRP)~.- TransmissionType - Hatchback,data=train)
summary(log.model2)
# Look at VIF
vif(log.model2)[,3]^2
# CityMPG has really high VIF remove it from model
log.model3 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG,data=train)
# Look at VIF
vif(log.model3)[,3]^2
# NumberOfDoors has really high VIF remove from model
log.model4 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG - NumberOfDoors,data=train)
# Look at VIF
vif(log.model4)[,3]^2
# HighwayMPG still have over 10 VIF, remove from model
log.model5 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG - NumberOfDoors - HighwayMPG,data=train)
vif(log.model5)[,3]^2
summary(log.model5)
# Diesel is not significant, HighPerformance is not significant, Performance is not significant Remove from simple model
log.model6 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG - NumberOfDoors - HighwayMPG - Diesel - HighPerformance - Performance,data=train)
vif(log.model6)[,3]^2
summary(log.model6)
# N_A is still not significant, remove from model
log.model7 = lm(log(MSRP)~.- TransmissionType - Hatchback - CityMPG - NumberOfDoors - HighwayMPG - Diesel - HighPerformance - Performance - N_A,data=train)
vif(log.model7)[,3]^2
summary(log.model7)
# Model 7 is a highly interpretable model with decent R-squared.
